Code for *Tree-Ring Evidence of Increasing Drought Risks amidst Projected Flood Intensification in the Kabul River Basin (Afghanistan and Pakistan)* by Khan et al. (2022)

### 2022-08-03 paper-code.Rmd
Add stepwise selection and clean up

```{r}
source('R/init.R')
source('R/input-selection-functions.R')
source('R/correlation_functions.R')
source('R/drought_analysis_functions.R')
```

@@

sv <- c(1, 2)
sPC <- as.data.table(PC[, sv, drop = FALSE])
lmFit <- PCR_reconstruction(PSepAug, sPC, firstYear, transform = 'none')
set.seed(42)
cvFolds <- make_Z(PSepAug$Qa, frac = 0.25, contiguous = TRUE)
lmCV <- cvPCR(PSepAug, sPC, firstYear, transform = 'none',
              Z = cvFolds, use.robust.mean = FALSE)
```

@@

```{r}
round(lmCV$metrics, 2)
```
**Figure S4 - score distribution**

>>>>

```{r}
source('R/init.R')
source('R/correlation_functions.R')
source('R/drought_analysis_functions.R')
```

@@

# Stepwise linear regression
DT <- cbind(PC[450:502, 1:3], Qa = PSepAug$Qa) |> as.data.frame()
step(lm(Qa ~ ., DT), direction = 'backward')
```

```{r}
# Build final model
sPC <- as.data.table(PC[, 1:2])
lmFit <- PCR_reconstruction(PSepAug, sPC, firstYear, transform = 'none')
set.seed(42)
cvFolds <- make_Z(PSepAug$Qa, frac = 0.25, contiguous = TRUE)
lmCV <- cvPCR(PSepAug, sPC, firstYear, transform = 'none',
              Z = cvFolds, use.robust.mean = FALSE)
```

@@

```{r}
round(lmCV$metrics[, 1:3], 2)
```
**Figure S4 - score distribution**
